Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils

### 2016-02-08 manuscript/cpcrw_manuscript.Rmd
Added first table!
…and sketched out others and figures

```{r, echo=FALSE}
library(dplyr, warn.conflicts = FALSE)
```

@@

```{r, echo=FALSE}
# compute outlier and exclusion numbers
sdn <- readLines("../outputs/summarydata.csv") %>% length
sdcn <- readLines("../outputs/summarydata_clean.csv") %>% length
en <- readLines("../outputs/2.5-remove/excluded_data.csv") %>% length
rn <- readLines("../outputs/2.5-remove/removed_data.csv") %>% length
```

Anomalous data were excluded based on their being more than 3.2 mean absolute deviations {Davies, 1993 #3138} from the treatment and temperature mean. We excluded `r en` of `r sdn` (`r round(en/sdn*100)`%) of the summarized samples for this reason. Other data (`r rn` of `r sdn`, `r round(rn/sdn*100)`%) were removed because of known instrument problems, e.g. the analyzer was left running after leaving a chamber. The final number of valid flux samples from the 100-day incubation was `r sdcn`.

@@

### Acknowledgments

@@

Table X. Summary of temperature, WC effects on gas fluxes.

Figure X. A faceted (Temperature ~ Treatment) plot showing normalized flux means and errors by incubation time. (Basically the figure already in the README diagnostics.)

Figure X. Core water content across the course of the experiment. (Basically the figure already in the README diagnostics.)

Figure X. A pairs plot of variable correlations?

>>>>

```{r, echo=FALSE, results='hide', message=FALSE, fig.keep='none'}
library(dplyr, warn.conflicts = FALSE)
setwd("../")
source("R/5-analyze.R")
```

@@

```{r, echo=FALSE}
# compute outlier and exclusion numbers
sdn <- readLines("../outputs/summarydata.csv") %>% length
sdcn <- readLines("../outputs/summarydata_clean.csv") %>% length
en <- readLines("../outputs/3-remove/excluded_data.csv") %>% length
rn <- readLines("../outputs/3-remove/removed_data.csv") %>% length
```

Anomalous data were excluded based on their being more than 3.2 mean absolute deviations {Davies, 1993 #3138} from the treatment mean on each day. We excluded `r en` of `r sdn` (`r round(en/sdn*100)`%) of the summarized samples for this reason. Other data (`r rn` of `r sdn`, `r round(rn/sdn*100)`%) were removed because of known instrument problems, e.g. the analyzer was left running after leaving a chamber. The final number of valid flux samples from the 100-day incubation was `r sdcn`.

@@

#### Acknowledgments

@@

#### References

**Table 1.** Summary of gravimetric water content effects on gas fluxes, by treatment and temperature.

```{r kable, echo=FALSE}
# Print out the `WC_effect` data frame in a nice-looking table
WC_effect$Gas[WC_effect$Gas == "CO2"] <- "CO<sub>2</sub>"  # html
WC_effect$Gas[WC_effect$Gas == "CH4"] <- "CH<sub>4</sub>"  # html
knitr::kable(WC_effect, digits = 3, 
             col.names = c("Treatment", "Temperature", "Gas", "R<sup>2</sup>", "Sigma", "P", "AIC"))
```

**Table 2.** Effect of temperature and WC on cumulative C fluxes for each gas.

**Figure 1.** Core water content across the course of the experiment. (Basically the figure already in the README diagnostics.)

**Figure 2.** A faceted (Temperature ~ Treatment) plot showing normalized flux means and errors by incubation time. (Basically the figure already in the README diagnostics.)

**Figure 3.** Cumulative fluxes over the incubation.
